Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
tweak 6.2

In an attempt to gain insight into the behaviour of the algorithms, we also
investigated a simpler setting comparing just \PathLAD and \GlasgowTwo. This
pair is of particular interest because they are the best ``medium-case''
algorithms that use strong and weak filtering during search respectively. We
used machine learning techniques to train a simple, human-understandable model
which is able to distinguish these cases with reasonable accuracy. The model
produced uses four rules:

@@

\noindent
The first and third rules here intuitively make sense: if \IncompleteLAD
filtering does well, it is likely that continuing with this kind of filtering
during search will be successful. The third rule also excludes using \PathLAD
on very dense pattern graphs, where locally all-different filtering is
expensive and weak. The second rule is less obvious: \PathLAD filtering is weak
on regular graphs, so this part of the rule is unsurprising, but the remainder
of the rule appears to be a round-about way of excluding large, dense target
graphs. Still, this model suggests that it could be worth exploring
\emph{dynamically} enabling or disabling locally all-different filtering during
search, based upon very simple features which could be recomputed as search
progresses and conditions change.

>>>>

To gain further insight into the behaviour of the algorithms, we
investigated what affects the relative performance of \PathLAD and \GlasgowTwo.
This pair is of particular interest because they are the best ``medium-case''
algorithms that use strong and weak filtering during search respectively. We
used machine learning techniques to train a simple, human-understandable model
which is able to distinguish these solvers and gives performance better than
always choosing one of them. The model uses four rules:

@@

\noindent
The first and third rules intuitively make sense: if \IncompleteLAD
filtering does well, it is likely that continuing with this kind of filtering
during search will be successful. The third rule also excludes using \PathLAD
on very dense pattern graphs, where locally all-different filtering is
expensive and weak. The second rule is less obvious: while \PathLAD filtering is
weak on regular graphs and it makes sense to exclude this case, the other
components appear to exclude large and dense target graphs. The model suggests
that it would be worth exploring \emph{dynamically} enabling or disabling
locally all-different filtering during search, based upon very simple features
which could be recomputed as search progresses and conditions change.

This provides an interesting insight into the behaviour of our algorithms, as
well as giving indications for future work.
